**Density Dependence**

### 2023-03-13 Rmd/report mac.Rmd
Included Kobe F-Yield

Version: 1.0 (07 March 2023)

Version: 1.1 (`r format(Sys.time(), '%d %B %Y')`)

@@

@@

**Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence and the associated reference points, and **Figure 21** shows the Kobe plots of the final 2050 distributions of biomass and yield.

>>>>

Version 1.0 (07 March 2023)

Version 1.1 (08 March 2023)

Version 1.2 (10 March 2023)

Version 1.3 (`r format(Sys.time(), '%d %B %Y')`)

@@

We then plotted the Kobe phase plot for 2050 with the associated density functions for F/Fmsy and Catch/MSY. Because there is no uncertainty included in the fishing mortality during the simulations, the marginal distributions of F do not exist in this plot.

fig_nums(
  name    = "kobe2", level = 1, display = FALSE,
  caption = "F Kobe plot for 2050 for base case (no DD) for all $F_{MSY}$'s (red is from the right scenario). Topleft: base, topright: M, bottomleft: MM, bottomright: MMM")

knitr::include_graphics(path=
                    c(file.path(figuresdir,paste("05",mystk,"kobe FY base.jpg",sep="_")),
                      file.path(figuresdir,paste("05",mystk,"kobe FY M.jpg",sep="_")),
                      file.path(figuresdir,paste("05",mystk,"kobe FY MM.jpg",sep="_")),
                      file.path(figuresdir,paste("05",mystk,"kobe FY MMM.jpg",sep="_"))
                      )
                    )

*`r fig_nums("kobe2")`*

@@

**Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence and the associated reference points, **Figure 21** shows the Kobe plots of the final 2050 distributions of biomass and yield and **Figure 22** the Kobe pltos for F and yield.
